Debugging by \textit{lastChange}

### 2010-10-25 papers/pldi2011/sigplanconf-template.tex
adding setVariableChangeHook to section 4.

\subsubsection{local, closure and \texttt{catch} scopes}
Local scope refers to the most nested scope in the scope
chain. Closure scope refers to the scope which is created once a
function is defined. Catch scope is the scope created in the catch
block of try-catch statements and contains the exception
variable. These scopes are not necessarily regular JavaScript
objects. Therefore, to track changes to a variable in these scopes we
use a different strategy.

Only operations in the scope of the these varibles can change their value; that includes the defining scope and scopes nested inside of them.
For example in Figure
~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
changed in lines 10 to 23. Therefore, after locating the function in
which the variable is defined, it is enough to parse the code inside
the function block and set a hook on all lines where the variable is
assigned a new value. \textit{What if we called this operation setVariableChangeHook() and defered the discussion to 4??}
We also set a hook at the first line of the function which is
corresponding to the line variable is defined. In Figure
~\ref{fig:js-closure}, if the execution is paused at line 17 and the
last change of \texttt{var1} is queried, two hooks on lines 16 and 17
will be set, but if the execution is paused at line 20 , four hooks on
lines 11, 12, 14, 20 will be set. These two cases are different due
the fact that \texttt{var1} in \texttt{firstChild} is a local variable
but in \texttt{secondChild} is a closure variable.

@@

Every time one of the hooks hits a new change event is inserted to the
list of change events. During execution the same variable might be
changed several times but in different scopes. Figure
~\ref{fig:recursive} demonstrates a case that the same variable
\texttt{x} is changed several times but in different scopes due to the
recursive calls. Without the scope id calling \textit{lastChange(x)}
at point C will return point B while the right answer is point A. To
address this issue, we employ \texttt{scopeId()} operation-explained
in the next section-which returns a unique id for a scopes during on
execution. The scope id is kept at every variable change event. Once
the execution reaches the reproduction point, using variable's scope
id, the last change is recognized.

@@

\subsection{Algorithm technical details}
\subsubsection{\texttt{objectId()} operation}
\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
It returns the value if this property is already defined,
otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
for each new \texttt{\_objectId} needed. \textit{CHECK THAT} To set
the property, we call the \texttt{defineProperty} standard JavaScript
function. \texttt{defineProperty} receives an argument which specifies
whether the property is enumerable or not. By setting the enumerable
field \texttt{false} for \texttt{\_objectId}, this property will not
apear in \texttt{for(property in object)} loops and therfore has no
effect on the program execution. Note that \texttt{\_objectId} is
not set for all objects but only those objects that need an id.

@@

>>>>

\subsubsection{local, closure and \texttt{catch} scopes}
Local scope refers to the most nested scope in the scope
chain. Closure scope refers to the scope which is created once a
function is defined. Catch scope is the scope created in the catch
block of try-catch statements and contains the exception
variable. These scopes are not necessarily regular JavaScript
objects. Therefore, to track changes to a variable in these scopes we
need a different approach.

All scopes in the scope chains come from blocks around the executing code.
Comparing the scope chain and the script we can identify the code block     % perhaps needs more explanation
(script) corresponding to the variable scope. Similar to \textit{lastChange} 
on object property, we define two basic operations \texttt{scopeId()} and
\texttt{setVariableChangeHook()}. The first one given an scope and its defining 
block(script) returns an integer as the scope's identifier. The second one 
given a callback function, a block(script) and a variable name, the function is called
whenever the variable is changed. After developer asks for the \textit{lastChange}
on a variable, in re-exeuction whenever the script is loaded, \texttt{setVariableChangeHook()}
is called. Every time the callback function is called a new change 
event is inserted to the list of change events.

@@

Figure ~\ref{fig:recursive} demonstrates a case that the same variable
\texttt{x} is changed several times but in different scopes due to the
recursive calls. Without considering the scopes calling \textit{lastChange(x)}
at point C will return point B while the right answer is point A. Using
\texttt{scopId()} operation, the scope id is also stored at every variable
change event.

After developer asks for the \textit{lastChange} on a variable, 
Once the execution reaches the reproduction point, using variable's scope
id, the last change is recognized (Figure ~\ref{fig:foo-changes2}).

@@

\subsection{Algorithm technical details}
\subsubsection{\texttt{objectId()} operation}
\texttt{objectId(obj)} first checks the argument \texttt{obj} for a property \texttt{\_objectId}.
It returns the value if this property is already defined,
otherwise it generates a new id and sets this property. The value of the id is simply an integer incremented 
for each new \texttt{\_objectId} needed. To set %\textit{CHECK THAT} 
the property, we call the \texttt{defineProperty} standard JavaScript
function. \texttt{defineProperty} receives an argument which specifies
whether the property is enumerable or not. By setting the enumerable
field \texttt{false} for \texttt{\_objectId}, this property will not
apear in \texttt{for(property in object)} loops and therfore has no
effect on the program execution. Note that \texttt{\_objectId} is
not set for all objects but only those objects that need an id.

@@

\subsubsection{\texttt{setVariableChangeHook()} operation}
Only operations in the scope of these varibles can change their value; 
that includes the defining scope and scopes nested inside of them.
For example in Figure ~\ref{fig:js-closure}, variable \texttt{var1} in line 11 can only be
changed in lines 10 to 23. Therefore, after locating the function in
which the variable is defined, it is enough to parse the code inside
the function block and set a hook on all lines where the variable is
assigned a new value. 
We also set a hook at the first line of the function which is
corresponding to the line variable is defined. In Figure
~\ref{fig:js-closure}, if the execution is paused at line 17 and the
last change of \texttt{var1} is queried, two hooks on lines 16 and 17
will be set, but if the execution is paused at line 20 , four hooks on
lines 11, 12, 14, 20 will be set. These two cases are different due
the fact that \texttt{var1} in \texttt{firstChild} is a local variable
but in \texttt{secondChild} is a closure variable.
